High-level cognition is supported by information-rich but compressible brain activity patterns

### 2023-12-22 paper/main.tex
added a significance statement, color bars to figs 6 and S5

@@

\caption{\textbf{Decoding accuracy and compression.} \textbf{A. Decoding
accuracy by number of components.} Ribbons of each color display
cross-validated decoding performance for each condition (intact, paragraph,
word, and rest), as a function of the number of components (features) used to
represent the data. For each condition, decoding accuracy has been normalized
by subtracting expected ``chance'' decoding performance (estimated as
$\frac{1}{T}$, where $T$ is the number of timepoints in the given condition).
This normalization was intended to enable fairer comparisons across conditions;
a relative decoding accuracy of 0.0 denotes ``chance'' performance. The
horizontal black line denotes 5\% decoding accuracy (used as a reference in
Panel B). \textbf{B. Numbers of components required to reach a fixed decoding
accuracy threshold, by condition.} The panel displays a zoomed-in view of the
inset in Panel A. Intersections between each condition's decoding accuracy
curve and the 5\% decoding accuracy reference line are marked by arrows. All
error ribbons in Panels A and B denote bootstrap-estimated 95\% confidence
intervals. \textbf{C. Estimating ``compressibility'' for each condition.} The
density plots display the numbers of components required to reach at least 5\%
(corrected) decoding accuracy, across all cross validation runs. For the
``rest'' condition, where decoding accuracy never reached 5\% accuracy, we
display the distribution of the numbers of components required to achieve the
peak decoding accuracy in each fold. (This distribution is nearly flat, as
also illustrated in Panel E.) \textbf{D. Estimating ``informativeness'' for each
condition.} The density plots display the peak (corrected) decoding accuracies
achieved in each condition, across all cross validation runs. \textbf{E.
Informativeness versus compressibility.} Each dot displays the minimum number
of components required to achieve at least 5\% corrected decoding accuracy
($x$-coordinate; for the rest condition the numbers of components are estimated
using the peak decoding accuracies as in Panel C) and the peak (corrected)
decoding accuracy ($y$-coordinate). The smaller dots correspond to individual
cross validation runs and the larger dots display the averages across runs. The
inset displays a zoomed-in view of the indicated region in the main panel.}

>>>>

\bigskip 
\noindent

\textbf{Significance Statement:} How our brains respond to ongoing experiences
depends on what we are doing and thinking about, how engaged we are, and our
past experiences, among other factors. To gain insights into how brain activity
patterns reflect ongoing cognitive processes, we examined two fundamental
aspects of brain activity under different cognitive circumstances:
informativeness and compressibility. Informativeness refers to the extent to
which brain patterns are both temporally specific and consistent across
different people. Compressibility refers to the extent to how robust the
informativeness of brain patterns is to dimensionality reduction. We found that
brain activity patterns evoked by higher-level cognitive tasks are both more
informative \textit{and} more compressible than activity evoked by lower-level
tasks. Our findings suggest that our brains flexibly reconfigure themselves to
optimize different aspects of how they function according to ongoing cognitive
demands.

@@

\caption{\textbf{Decoding accuracy and compression.} \textbf{A. Decoding
accuracy by number of components.} Ribbons of each color display
cross-validated decoding performance for each condition (intact, paragraph,
word, and rest), as a function of the number of components (features) used to
represent the data. For each condition, decoding accuracy has been normalized
by subtracting expected ``chance'' decoding performance (estimated as
$\frac{1}{T}$, where $T$ is the number of timepoints in the given condition).
This normalization was intended to enable fairer comparisons across conditions;
a relative decoding accuracy of 0.0 denotes ``chance'' performance. The
horizontal black line denotes 5\% decoding accuracy (used as a reference in
Panel B). \textbf{B. Numbers of components required to reach a fixed decoding
accuracy threshold, by condition.} The panel displays a zoomed-in view of the
inset in Panel A. Intersections between each condition's decoding accuracy
curve and the 5\% decoding accuracy reference line are marked by arrows. All
error ribbons in Panels A and B denote bootstrap-estimated 95\% confidence
intervals. \textbf{C. Estimating ``compressibility'' for each condition.} The
probability density plots display the numbers of components required to reach
at least 5\% (corrected) decoding accuracy, across all cross validation runs.
For the ``rest'' condition, where decoding accuracy never reached 5\% accuracy,
we display the distribution of the numbers of components required to achieve
the peak decoding accuracy in each fold. (This distribution is nearly flat, as
also illustrated in Panel E.) The scale bar denotes a height of 0.01.
\textbf{D. Estimating ``informativeness'' for each condition.} The probability
density plots display the peak (corrected) decoding accuracies achieved in each
condition, across all cross validation runs. The scale bar denotes a height of
0.01. \textbf{E. Informativeness versus compressibility.} Each dot displays the
minimum number of components required to achieve at least 5\% corrected
decoding accuracy ($x$-coordinate; for the rest condition the numbers of
components are estimated using the peak decoding accuracies as in Panel C) and
the peak (corrected) decoding accuracy ($y$-coordinate). The smaller dots
correspond to individual cross validation runs and the larger dots display the
averages across runs. The inset displays a zoomed-in view of the indicated
region in the main panel.}
